Experiment 2 of 4

### 2016-10-02 experiments/e2/writeup/e2.Rmd
deleting from e2 some files that dont belong in master

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(knitr); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R') 
```

@@

```{r getData, echo=T}
rawdata <- read.table('data.txt', sep=' ')
```

```{r}
tempdata <- perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data
rtdata <- tempdata
bldata <- tempdata
```

@@

```{r computeSummariesForGraphs, cache=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", withinvars=c("Condition", "Vagueness", "Number", "Item"), idvar="Subject")
```

```{r rtplot, fig.width=5, fig.height=3, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, fill=Vagueness)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(pch=21, size=3, position=dodge) +
  #scale_shape_manual("",values = c(22, 22)) +
  scale_fill_manual("",values=c("black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="top",
        aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number)
rtplot
```

>>>>

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(Matrix); library(knitr); library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R'); source('e2-preprocessing.R')
```

```{r preprocessing}
source('e2-preprocessing.R')
if( !file.exists('e2-b-data.txt') ) {
  dat <- gatherData() 
  dat <- declareImpossibleRT(dat)
  #dat <- removeImpossibleTrials(dat)
  dat <- subset(dat, select=c(Subject, Trial, Item, c_Itm, 
                              discriminability, 
                              Instruction,
                              nchar_instr,
                              Vagueness, Number, Order, Quantity, 
                              c_Vag, c_Num, c_Ord, c_Qty,
                              NaType, response_category, 
                              isBorderline, RT, RT_log)
  )
  write.table(dat, file='e2-b-data.txt', sep='\t', quote=FALSE, row.names = FALSE)
}
```

@@

```{r getData, echo=T}
rawdata <- read.delim('e2-b-data.txt')
tempdata <- perSubjectTrim.fnc(rawdata[complete.cases(rawdata),], response='RT', subject='Subject', trim = 2.5)$data
rtdata <- tempdata
bldata <- tempdata
```

@@

```{r computeSummariesForGraphs, cache=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, 
                                measurevar="RT_log", 
                                withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
```

```{r rtplot, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, fill=Vagueness)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(pch=21, size=3, position=dodge) +
  #scale_shape_manual("",values = c(22, 22)) +
  scale_fill_manual("",values=c("black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="top",
        aspect.ratio=1,
        #axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number)
rtplot
```
